Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy

### 2017-02-28 paper/letter.tex
latest version

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Possible kinematics of an atypical Lyman-$\alpha$ dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different models: 
an interstellar medium composed by outflowing clumps with additional
random motions and an homogeneous gaseous sphere undergoing bulk rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the high
velocities postulated in our model, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.6\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model\label{multiphaseresults}.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.}  
\end{center}
\end{figure*}

@@

The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.  {\bf These parameters are: MAX}

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We then build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models, and then select for further analysis the best
$1\%$ models according to the lowest $\chi^2$ values.
The
$\chi^2$ gap in those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$.
The total number of degrees of freedom is $104$.

@@

The best values for the influential parameters correspond to
the values that produce the minimum
$\chi^2$.
The 1-$\sigma$ uncertainty comes from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.  
%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
%$P_{\rm cl}$

@@

The analytical solution for the rotation sphere is the base to
perform a Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model. For each time, the code calculates the likelihood of the
combination with respect to the observational data. The walkers explore
the parameter space sampling the likelihood function built as $\propto
\exp(\chi^2/2)$, where the $\chi^2$ is computed from each bin in the
spectra after normalization.

@@

Figure 1. summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the multiphase model (thick line). 
and the rotating homogeneous gas sphere (thin line).

In spite of the simplicity of our models, this is the first time that
the main \tol\ features can be reproduced: a wide, centered,
single-peaked \lya\ line.
This result does not demonstrate that our models are unique to
reproduce \tol's features, but is a significant step forward to
understand why this source is atypical.

\subsection{Multiphase ISM}
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

From this test we found that only three parameters influence the
$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
$10^{-4}$) and the probability that the \lya\ emission comes from the
clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
parameters do not influence the resulting spectra at all; it means
that they cannot be constrained from \tol's observations.

Qualitatively as \tol\ possesses a very wide spectrum which can be
achieved by subsequent scatterings off (relatively) fast moving clumps
while the multi-phase nature (i.e., the existence of low-density
channels) ensures the high flux at line center as observed.

@@

The results are summarized in 
Figure \ref{emceeresults}. 
From this model we find that the fiducial 
parameters that could explain the broad features in \tol\ are 
$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
degrees.

The best parameters in the rotation model are a rotational velocity of 
$V_{\rm max}=348^{+75}_{-48}$ \kms, a neutral Hydrogen optical depth of 
$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.  
This model is also able to constrain the angle between the plane
perpendicular to the rotation axis and the observational line-of-sight
to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

@@

Having constrains for  velocity dipersion $\sigma$ of some dynamical
tracers (clumps in the case of the multiphase model) in a spherical
system located in a region of size $r$ we estimate the dynamical mass
within $r$.

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}

We use the 3D half-luminosity
radius, $r_{s}$, as the typical size for the HI region.

In the case of rotational velocity $v$ in a region of size $r$ we
estimate the dynamical mass by

\begin{equation}
M_{\rm dyn} = \frac{v ^{2}r}{G} = 1.16\times10^{9}
\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot} 
\end{equation}

In the multiphase model the best constrained parameters by the
observational data are the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump ,  the clump's outflowing velocity
$v_{\infty, \rm{cl}}=$\inftyclump\ and the fraction of the
\lya\ emission that is  coming from the cold clumps  $P_{\rm cl}=$\probaclump.

Assuming that the clumps are located in a spherical region of radius
$r_s=2.25$ kpc (corresponding to \tol's estimated 3D half-luminosity
radius), 
this corresponds to dynamical masses of $M_{\rm dyn} =
3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$ and $M_{\rm
  dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$ for the
rotation and multiphase models, respectively,

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$. 
\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
rotation estimate.

We lean towards the lower dynamical mass estimate from the multiphase
model as it seems easier to reconcile with the following two
astrophysical mechanisms for its origin.
The first way to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
leaves open the question as to why  \tol\ is not more similar to the
Milky Way galaxy as it would be hosted by a dark matter halo of similar
mass. 
A second possibility is that \tol\ hosts a supermassive black hole of
$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
than the supermassive black hole found in the compact dwarf galaxy
M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
as \tol. This would leave open the question about the formation
process of such a system.

Another perspective to appreciate the atypically high dynamical mass
estimates comes from the observed scaling relations for dwarf
galaxies.
Assuming that \tol\ followed the fundamental plane relationship
between its mean surface brightness $I_e$, the projected half-light
radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
the expected velocity dispersion should be on the order of $5 \pm 1$ 
\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
results from the multiphase and rotation models, respectively. 
These are equivalent to factors of $\sim$ $100$ - $3600$ on the
dynamical mass.
Once again,  \tol\ seems to be significantly more massive than
expected.

@@

In this paper we presented two theoretical models that explain the main
observational feature of \tol, which have been unexplained so far.
One model is based on a multiphase ISM and the other on gas rotation,  
It is the first time that an observed \lya\ profile can be fully
reproduced by either of these two conditions.
Furthermore, the kinematics of both models suggest a dynamical mass
ten times larger than the baryonic mass infered from observations.

A new observational test is needed to clarify the physical nature of
\tol. 
We suggest that integral field unit measurements spatially
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}.

@@

These findings demonstrate the importance of including rotation and multiphase
conditions as features to model the \lya\ line in high redshift
galaxies.
Additionally, if the hypothesis of a supermassive black
hole in \tol\ proves to be consistent with future observational
kinematic maps, it could correspond to a so far undetected
supermassive black hole in a dwarf galaxy, providing a new way to test
and probe theories on the co-evolution of galaxies and black holes in
the first generation of galaxies.

\section*{Acknowledgments}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe.    
Before the observational detection of the first galaxies becomes
reality, CDGs are the best systems to test our ideas on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work demonstrates the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$, which also include information about the spatial
distribution and thermal state of the clumps and the intraclump
medium.

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}

where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the $\chi^2$ gap in those $25$ models is close to
$\Delta\chi^2 = 3000$, the lowest $\chi^2$ being close to
$\chi^2_{min}=1200$.
To have a sense of scale, the total number of degrees of freedom is
$104$.

@@

The best values for the influential parameters correspond to
the values that produce the minimum
$\chi^2$.
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the influential parameters around its
corresponding minimum.   
%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
%$P_{\rm cl}$

@@

The analytical solution for the rotation sphere is the base to
perform a Markov Chain Monte Carlo (MCMC) calculation using the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
ensemble sampler for MCMC. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model.
For each timestep, the code calculates the likelihood of the
combination with respect to the observational data.
The walkers explore
the parameter space sampling the likelihood function built as $\propto
\exp(\chi^2/2)$, where the $\chi^2$ follows the definition in Equation
\ref{eq:chi2}.

@@

Figure 1. summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the
multiphase model (thick line)  and the rotating homogeneous gas sphere
(thin line).

In spite of the simplicity of our models, this is the first time that
the main \tol\ features can be reproduced: a wide, centered,
single-peaked \lya\ line.
This result does not demonstrate that the kinematic features we
include in our models are necessary to reproduce \tol's features, but
at least they show that they are a sufficient condition.
This is a significant step forward to understand the influence that
different kinematics have in producing the atypical line profile shown
by \tol.

In what follows we summarize the values of the kinematic parameters
that managed to explain \tol\'s \lya\ profile.

From the K-S tests we find that only three parameters can be
constrained by the observations: the clump outflow velocity
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), the clump velocity
dispersion $\sigma_{\rm cl}$ (p-value $10^{-4}$) and the probability
that the \lya\ emission comes from the clumps $P_{\rm cl}$ (p-value
$10^{-4}$).
This does not mean the other parameters do not influence the resulting
spectra at all; it means that they cannot be constrained from \tol's
observations.

The results are summarized in Figure \ref{multiphaseresults}.
Left panels show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2$. 
The right panel shows the actual $\chi^2$ values and its corresponding
parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

Qualitatively, as \tol\ possesses a very wide spectrum which can be
achieved by subsequent scatterings off (relatively) fast moving clumps
while the multi-phase nature (i.e., the existence of low-density
channels) ensures the high flux at line center as observed.
A lower velocity dispersion would produce a thiner line than the
observed.
From the lower right panel in \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

@@

The results are summarized in  Figure \ref{emceeresults}. 
From this analysis we find that the best parameters in the rotation
model are a rotational velocity of  $V_{\rm max}=348^{+75}_{-48}$
\kms, a neutral Hydrogen optical depth of
$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium
temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
This model is also able to constrain the angle between the plane
perpendicular to the rotation axis and the observational line-of-sight
to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

Lower rotational velocities are disfavored by the fact that the line
is single peaked.
Fixing the optical depth at a high value of $10^7$ ensures that the line width
is close to its observed value.
A lower rotational velocity would produce a double peaked line.
The fact that the velocity and optical depth priors were wide enough,
allows us to think that the current values found by the MCMC are
robust given the observational constraints.

@@

Using the constrains for the velocity dipersion $\sigma$ and the
maximum rotational velocity $V_m$ in a spherical system localized in a
region of size $r$ we can estimate two different values for the
dynamical mass within $r$:

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
M_{\odot}, 
\end{equation}
%
and
%
\begin{equation}
M_{\rm dyn} = \frac{V_m ^{2}r}{G} = 1.16\times10^{9}
\left(\frac{V_m}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot}, 
\end{equation}
%
for the multiphase and rotation model, respectively.
Assuming that the \lya\ emission is entirely powered by star formation 
we use the 3D half-luminosity radius $r_s=2.25$ kpc as the typical size
for the HI region,

In the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, while the
rotational velocity of $V_{\rm max}=348^{+75}_{-48}$\kms corresponds
$M_{\rm dyn} = 3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$.

\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$. 
\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
the baryonic mass, depending if one considers the multiphase or
bulk rotation estimate. 
We lean towards the lower dynamical mass estimate from the multiphase
model as it seems easier to reconcile with the following two
astrophysical mechanisms for its origin.

A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
leaves open the question as to why  \tol\ is not more similar to the
Milky Way galaxy as it would be hosted by a dark matter halo of similar
mass.

A second possibility is that \tol\ hosts a supermassive black hole of
$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
than the supermassive black hole found in the compact dwarf galaxy
M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
as \tol. This would leave open the question about the formation
process of such a system.

%Another perspective to appreciate the atypically high dynamical mass
%estimates comes from the observed scaling relations for dwarf
%galaxies.
%Assuming that \tol\ followed the fundamental plane relationship
%between its mean surface brightness $I_e$, the projected half-light
%radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
%I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
%the expected velocity dispersion should be on the order of $5 \pm 1$ 
%\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
%results from the multiphase and rotation models, respectively. 
%These are equivalent to factors of $\sim$ $100$ - $3600$ on the
%dynamical mass.
%Once again,  \tol\ seems to be significantly more massive than
%expected.

A new observational test is needed to clarify the kinematical nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol\. This lack of observations also puts an upper
limit on the intensity of recent black hole activity.

Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}. 
recent

@@

In this paper we presented two kinematic models that independently
reproduce the so far unexplained observational features of \tol's
\lya\ emission line.

One model is based on a multiphase ISM with random clump motions and
the other on gas bulk solid body rotation.
It is the first time that an observed \lya\ profile can be fully
reproduced by either of these two kinematic conditions.
Furthermore, the kinematics of both models suggest a dynamical mass
at least ten times larger than the baryonic mass infered from observations.
We suggest that additional integral field unit observations are the
only way to be certain about the detailed kinematic structure in \tol.

@@

These findings demonstrate the importance of including rotation and multiphase
conditions as kinematic features to model the \lya\ line in high redshift
galaxies.
Additionally, if the hypothesis of a supermassive black
hole in \tol\ proves to be consistent with future observational
kinematic maps, it could correspond to a so far undetected
supermassive black hole in a dwarf galaxy, providing a new way to test
and probe theories on the co-evolution of galaxies and black holes in
the first generation of galaxies.

\section*{Acknowledgments}
We thanks J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data in electronic format. This data was used to prepare Figure
1.
